---
title: "Kaggle: House Price Project"
author: "Yunus Kamal"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    gallery: true
    lightbox: true
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="200", width = "400")
```


##Importing Data and Initializing Libraries

###Loading Libraries
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(DT)
source("EDA Functions.R")
```

###Loading Datasets
```{r, echo=TRUE, message=FALSE, warning=FALSE}
test<-read_csv("Data/test.csv")
train<-read_csv("Data/train.csv")

datatable(train)
```

##Exploratory Data Analysis: Numeric

###Checking Variables Data Type
```{r}
data_type<-as.data.frame(sapply(train,function(x) class(x)))
colnames(data_type)<- c("Data Type")

datatable(data_type)
```

###Changing Data type as per Documention
```{r, message=FALSE, warning=FALSE}
attach(train)
change_chr<-c("MSSubClass","OverallCond","OverallQual")

train[,change_chr] = apply(train[,change_chr],2,function(x) as.character(x))

str(train[,change_chr])

```

###Numeric Columns Summary 
```{r}
EDA_num_Summary<-Summary_num(train)
datatable(EDA_num_Summary,options = list(autoWidth = TRUE))
```

###Number of Numeric & Character Data
```{r}
Count_Type(train)
```


###Numeric Column Density Plots
```{r, message=FALSE, warning=FALSE}
Univariate_num(train,outlier_flag = 1)
```

###Numeric Column Bivariate Analysis
```{r, message=FALSE, warning=FALSE}
Bivariate_num(train,dep="SalePrice",outlier_flag = 1)
```

##Exploratory Data Analysis: Character

###Character Columns Summary
```{r, message=FALSE, warning=FALSE}
EDA_char_Summary<-Summary_char(train)
datatable(EDA_char_Summary,options = list(autoWidth = TRUE))
```

